Predictors of frog survival following translocations - supplemental analyses

### 2023-05-17 code/translocation_survival_analysis_supp.Rmd
Edit axis labels

d1 %>% 
  mutate(period = factor(period, levels = c("before", "after"))) %>% 
  ggplot(aes(x = period, y = log10(bd_load + 1))) +
    geom_boxplot() + 
    labs(x = "Period", y = "Bd load (log10(bd_load + 1))") +
    facet_grid(. ~ site_id1) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5),
          strip.text.x = element_text(size = 8),
          panel.grid = element_blank())
ggsave(here::here("doc", "manuscript", "figures", "bdload_beforeafter.png"), width = 6, height = 3)
```

>>>>

d1 %>% 
  mutate(period = factor(period, levels = c("before", "after"))) %>% 
  ggplot(aes(x = period, y = log10(bd_load + 1))) +
    geom_boxplot() + 
    labs(x = "Period (relative to translocation)", y = (expression(Bd~load~(log["10"]~copies+1)))) +
    facet_grid(. ~ site_id1) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5),
          strip.text.x = element_text(size = 8),
          panel.grid = element_blank())
ggsave(here::here("doc", "manuscript", "figures", "bdload_beforeafter.png"), width = 6, height = 3)
```
